Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-08-23 Manuscript/manuscript.tex
Add references to intor

\todo{SAMULI: I can write preliminary version of the introduction asap.}

>>>>

Lipids with negatively charged headgroups, like phophatidylserine
play important role in biomembranes. Signaling domains interact with
anionic lipid membranes due to electrostatic and specific interactions
with negatively charged lipids \cite{lemmon08,leventis10}.
Anionic lipids and their interactions with ions play also role in membrane
fusion \cite{??}. \todo{Pavel can probably improve this and give a citation}
These interactions depend on
chemical details of lipid headgroups and binding of counter and co-ions
to anionic membranes.

Various interaction schemes have been proposed for the negatively charged
lipids with ions and other lipids. Some studies suggest that the
binding constant to negatively charged lipids is similar to zwitterionic
and the binding affinity is increased only due to the increased cation
concentration in the vicinity of the membrane \cite{seelig90,sinn06}.
On the other hand, calcium forms dehydrated complexes with PS headgroups
which cause phase separation \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Different theories are difficult to evaluate experimentally,
especially with physiological ion concentrations which are typically quite low.

Spectroscopic experiments give detailed information about the
interactions between ions and PS lipids, but the data is often indirect and difficult to
interpret \cite{hauser77,kurland79,eisenberg79,hauser83,dluhy83,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Classical molecular dynamics (MD) simulations give
access to all the details, but the current force fields are not
sufficiently accurate to interpret the interactions between anionic
lipid headgroups and other lipids or ions \cite{NMRlipidsIV}.
Implicit inclusion of electronic polarizability using
electronic continuum correction (ECC) to lipid models
substantially improved the interactions between cations and
zwitterionic lipids \cite{melcr18}. Here, we extend the approach
to anionic PS lipids to more accurately describe their interactions with ions
and PC headgroups in mixed lipid bilayers. The results pave
the way for more realistic MD simulations of negatively charged
lipid bilayers to be used in wide range of applications.
